%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-red}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}
% \definecolor{sectiondivider}{HTML}{5D5D5D}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
%\photo[circle,noedge,left]{./examples/profile}
\name{Fabian}{Bull}
\position{Software Architect}
\address{Mandolinenweg 8a, 06128 Halle (Saale), Germany}

\mobile{(+49) 162 3042488}
\email{fabian@fbull.de}
%\dateofbirth{January 1st, 1970}
\homepage{fbull.de}
\github{peri4n}
% \linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
\twitter{@peri4n}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \kaggle{kaggle-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra information}

\quote{``Be the change that you want to see in the world."}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient
  {Company Recruitment Team}
  {Google Inc.\\1600 Amphitheatre Parkway\\Mountain View, CA 94043}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer}
% How the letter is opened
\letteropening{Dear Mr./Ms./Dr. LastName,}
% How the letter is closed
\letterclosing{Sincerely,}
% Any enclosures with the letter
\letterenclosure[Attached]{Curriculum Vitae}


%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal information
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[R]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Fabian Bull~~~·~~~Cover Letter}
  {}

% Print the title with above letter information
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{The position you are pursuing}
State immediately the position you are pursuing and how you came to know of the opening.
If you have an alumnus, family or other contact at the organization, you can mention that here as well.
Tell the employer briefly (one or two sentences) why you are interested in this position.

\lettersection{About Me}
Explain the skills and experiences you have that will make you successful in that position.
Talk about class you have taken, activities you have been involved in, summer experiences you have had.
You do not have to have directly related experience but think about the skills you have gained from what
  you have done and how those could relate to duties of the position you are applying for.
You do not want to repeat your resume to the employer in this paragraph but this is the place to highlight
  related accomplishments that will make the reader want to learn more, which will lead them to your resume.
The goal is to show the employer that you have the confidence in your ability to succeed in the position.

\lettersection{Why Google?}
Demonstrate tnat you have done some research about this organization.
Go to their web site, look in industry periodicals (Ad Week, Wall Street Journal, Chronicle of Higher Education)
  and talk to alumni or other contact that may currently work for the organization.
This research does not have to be extensive but it shows that you have taken some time to think about the position
  and put some effort into this letter.
This makes a very good impression on employers.
It shows that his is not a form letter where only the address and contact name is changed for each position.

\lettersection{Why Me?}
Duis sit amet magna ante, at sodales diam. Aenean consectetur porta risus et sagittis. Ut interdum, enim varius pellentesque tincidunt, magna libero sodales tortor, ut fermentum nunc metus a ante. Vivamus odio leo, tincidunt eu luctus ut, sollicitudin sit amet metus. Nunc sed orci lectus. Ut sodales magna sed velit volutpat sit amet pulvinar diam venenatis.

\lettersection{Closing}
State that you would welcome a personal interview to further discuss this opportunity.
If you need to explain anything out of the ordinary on your resume, this is the place to do it.
You might mention that if you do not hear anything from the potential employer in two to three weeks time
  that you will call to follow up this letter to se where they are in their process.
Finish by thanking them for their attention and express a desire to meet them sometime in the near future.

\end{cvletter}

%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter information
\makeletterclosing

\end{document}
